Bayesian estimation of chronic disease epidemiology from incomplete data

### 2018-06-26 vignette.Rmd
vignette edits

This approach is used in the DisMod-MR software, as explained by @flaxman2015, however the software itself is undocumented and not fully published.  The older (published) DisMod II (@dismod2) used an optimisation approach to estimate parameters, which is a less statistically-principled rough approximation.  Other advantages of the Bayesian method include

@@

and we wish to estimate case fatality by age, given these inputs.

The first few rows of the full data frame are shown here.  The estimates from DisMod II are given in the variable `cfout`.  The other variables are explained below.

>>>>

This approach is used in the DisMod-MR software, as explained by @flaxman2015, however the software itself is undocumented and not fully published.  The older (published) DisMod II (@dismod2) used an ad-hoc optimisation approach to estimate parameters.

Advantages of the Bayesian method include

@@

and we wish to estimate case fatality by age, given these inputs.  The first few rows of the full data frame are shown here.  The estimates of case fatality from DisMod II are given in the variable `cfout`.  The other variables are explained below.
